---
title: "Baby Names"
author: "YOUR NAME HERE"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

```{r libraries}
library(tidyverse)
library(modelr)
```



# The Data

Our dataset in this lab concerns baby names and their popularity over time.  The dataset `babies_ca` has information about baby names in California from 1940-2016.  For each year, and for each name with at least 50 recorded babies born, we are given the counts of how many babies had that name. 

For now, we will study only the name "Kelly".  First we read in that data:

```{r, include = FALSE}

rachels = read.csv("babies_ca.csv") %>%
  filter(Name %in% c("Rachel"))

```


# Trend in Kellys over time

Let's take a look at how the name "Kelly" has changed over time.  The following code will plot the counts for each year.

```{r plot}

ggplot(rachels, aes(x = Year, y = Count)) + geom_line()

```


Trend by Gender

```{r plot}

ggplot(rachels, aes(x = Year, y = Count, color = Gender)) + geom_line()

```


# Is my name not cool any more?

I was born in 1989.  Let's look at only the time frame since I was named.

```{r filter}
rachels_98 <- rachels %>%
  filter(Year >= 1998)
```

We will create a linear model with the year as the explanatory variable, and the number of Kellys as the response.

```{r model, echo = FALSE}
my_model <- lm(Year ~ Count, data = rachels_98)

summary(my_model)
```


Let's plot this linear model.

```{r plot}

ggplot(rachels_98, aes(x = Year, y = Count)) +
  geom_point() + 
  stat_smooth(method = "lm")

```

We should also check out the *residuals*.  

```{r residuals}

rachels_98 <- rachels_98 %>%
  add_predictions(my_model) %>%
  mutate(residual = Count - pred)

ggplot(rachels_98, aes(x = Year, y = residual)) + geom_point()
```


What about by gender?
#doesnt work because only female rachels
```{r gender model}
my_model_2 <- lm(Count ~ Year*Gender, data = kellys_89)

summary(my_model_2)

ggplot(kellys_89, aes(x = Year, y = Count, color = Gender)) + geom_point() + stat_smooth(method = "lm")

kellys_89 <- kellys_89 %>%
  add_predictions(my_model_2) %>%
  mutate(
    residual = Count - pred
  )

ggplot(kellys_89, aes(x = Year, y = residual, color = Gender)) + geom_point()
```


## Conclusion
