---
title: "Lab 4"
author: "Rachel Loh"
date: "2-14-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(stringr)
songs <- read.table("https://www.dropbox.com/s/jrwjthqo9b5o07g/billboard_songs.txt?dl=1", header = TRUE, stringsAsFactors = FALSE)
```

```{r}
songs <- songs %>%
  mutate(year = as.numeric(str_sub(chart.date, start = 1, end = 4)),
         month = as.numeric(str_sub(chart.date, start = 5, end = 6)),
         day = as.numeric(str_sub(chart.date, start = 7, end = 8)), 
         date_time = make_datetime(year = year, month = month, day = day,
                                   hour = 0L, min = 0L, sec = 0))
```


What 10 songs spent the longest on the charts? Give only the title, artist, and weeks.

The songs in the dataset below spent the longest time on the charts.

```{r}
songs %>%
  arrange(desc(weeks.on.chart))%>%
  top_n(10, weeks.on.chart) %>%
  select(title, artist, weeks.on.chart)

```
What date did the oldest song(s) in this dataset leave the charts? Give only the date.

July 27th, 1940
```{r}
songs %>%
    arrange(date_time) %>%
    slice(1L) %>%
    mutate(weekchart = weeks(as.numeric(weeks.on.chart)),
           how_long = date_time + weekchart) %>%
    select(how_long)
```
What songs could have been played at your 16th birthday party? That is, which songs that eventually peaked at #1 entered the charts within a couple months (before or after) your 16th birthday? Give only the song title, artist, and date of chart entry.

Fancy, All of Me, Happy, and Dark Horse could have been played.
```{r}
songs %>%
  select(title, artist, date_time, overall.peak) %>%
  filter(overall.peak == 1) %>%
  filter(ymd(20140821) <= date_time & date_time <= ymd(20150121))
```


What is the most common word, at least 4 letters long, used in the title of any song? Give only the word itself, and its count.

Heart is the most common word used.
```{r}
string_title <- toString(songs$title)

new_title <- string_title %>% 
  str_remove_all(pattern = "([:punct:])") %>%
  str_extract_all("\\w+")%>%
  unlist()

vector_titles <- new_title[nchar(new_title) > 4]

data.frame(vector_titles) %>%
  group_by(vector_titles) %>%
  summarise(total_count = n()) %>%
  top_n(1, total_count)



```

Which five artists were the most successful in terms of:

Number of songs that were #1 hits
Elvis Presley, Madonna, Mariah Carey,
Michael Jackson, The Beatles

Total weeks any of their songs spent on the chart.
Elvis Presley:1284
Madonna:870
Mariah Carey:576
Michael Jackson:573
The Beatles:628

```{r}
songs %>%
  select(artist, overall.peak) %>%
  filter(overall.peak == 1) %>%
  group_by(artist) %>%
  summarise(num_one = n()) %>%
  top_n(5, num_one)


songs %>%
  select(title, artist, weeks.on.chart) %>%
  group_by(artist) %>%
  summarise(total_weeks = sum(weeks.on.chart)) %>%
  filter(artist == "ELVIS PRESLEY" | artist == "MADONNA" | artist == "MARIAH CAREY" | artist == "MICHAEL JACKSON" |artist == "THE BEATLES") %>%
  top_n(5, total_weeks)
  
  

```

Let’s take a look at artists who work together on songs.

Which artist has featured on the most Billboard charting songs?

Lil Wayne

Which artist has collaborated on the most Billboard charting songs?

His Orchestra

```{r}
artist_feat <- str_subset(songs$artist, pattern = "(featuring)+")
artist_feat <- sub(".*featuring", "", artist_feat)
artist_feat <- str_split(artist_feat, pattern = "&")
artist_feat <- unlist(artist_feat)
artist_feat <- str_trim(artist_feat, side = "both")
artist_feat <- as.data.frame(artist_feat)
artist_feat %>%
  group_by(artist_feat) %>%
  summarise(count = n()) %>%
  top_n(1, count)
  
artist_collab <- str_subset(songs$artist, pattern = "[,&]+")
artist_collab <- str_split(artist_collab, pattern = "&")
artist_collab <- unlist(artist_collab)
artist_collab <- str_remove_all(artist_collab, pattern = "(feat)(uring)?.*")
artist_collab <- str_trim(artist_collab, side = "both")
artist_collab <- data_frame(artist_collab)
artist_collab %>%
  group_by(artist_collab) %>%
  summarise(count = n()) %>%
  top_n(1, count)
```





